Crosslinguistic Word Orders Enable an Efficient Tradeoff between Memory and Surprisal

### 2019-03-17 paper.tex
revising

We estimate the quotient
\begin{equation}
	G :=	\frac{\E_{x \sim P_1}[W_+(x)]}{\E_{x \sim P_1}[W_+(x) + W_-(x)]}
\end{equation}
where $P_1$ is the distribution over values obtained for real orderings.
We use a bootstrapped confidence interval for $\E[G]$ for quantifying the degree of optimization.
For bootstrapping, we separately resample samples from the real language and from the baseline grammars.

@@

In Figure~\ref{tab:plain-results} (TODO), we show the estimated memory-surprisal tradeoff curves.

In Figure~\ref{tab:medians}, we show the medians.

@@

- show the slice histograms

- show the total histogram

@@

\paragraph{Inferential Statistics}

inferential

- report the bootstrapped thing G

Median Differences \ref{tab:median_diffs}

Quantiles \ref{tab:quantiles}

@@

In all but X languages $\E[G] > 0.5$ significantly.

$\E[G]$ was not estimated to be significantly above $>5$ for four languages: Latvian, North Sami, Polish, and Slovak.

%\begin{longtable}{llllllllllllllllll}
	%\input{results-table-word-level.tex}
%\end{longtable}

>>>>

We estimate the quotient
\begin{equation}\label{eq:g}
	G :=	\frac{\E_{x \sim P_1}[W_+(x)]}{\E_{x \sim P_1}[W_+(x) + W_-(x)]}
\end{equation}
where $P_1$ is the distribution over values obtained for real orderings.
We use a bootstrapped confidence interval for $\E[G]$ for quantifying the degree of optimization.
For bootstrapping, we separately resample samples from the real language and from the baseline grammars.

@@

In Figure~\ref{tab:plain-results} (TODO), we show the estimated memory-surprisal tradeoff curves for all samples.

In Figure~\ref{tab:medians}, we show the medians for real and baseline languages.

@@

In Figure~\ref{tab:slices}, we show the distribution of surprisals achieved at the maximal memory value for real and random languages.

In Figure~\ref{tab:hist-real}, we show surprisals at maximum memory, after z-transforming for each individual language and then aggregating.

In Table \ref{tab:median_diffs}, we show the differences in median surprisal, as a function of memory.

In Table~\ref{tab:boot-g}, we report the bootstrap estimates and confidence intervals for G~(\ref{eq:g}).
$\E[G]$ was not estimated to be significantly above $>5$ for four languages: Latvian, North Sami, Polish, and Slovak.

In Table~\ref{tab:quantiles}, we show the quantiles.

@@

@@
